The Hosting Environment of the Advanced Resource Connector middleware

### 2008-08-05 doc/hed/ARCHED_article.tex
End of day check in.

\usepackage{ifthen}
\newboolean{brieftechdesc}
\newboolean{verbtechdesc}
\setboolean{brieftechdesc}{true}
\setboolean{verbtechdesc}{false}

@@

\ifthenelse{\boolean{verbtechdesc}}{
This is a verbose test text. It might not seem verbose but it is.
}{}

\paragraph{TLS MCC}

>>>>

\usepackage{ifthen}
\newboolean{brieftechdesc}
\newboolean{verbtechdesc}
\setboolean{brieftechdesc}{false}
\setboolean{verbtechdesc}{true}

@@

\ifthenelse{\boolean{verbtechdesc}}{
This MCC can be configuered with one or more \texttt{<tcp:Listen>} elements which in turn contain the elements \texttt{<tcp:Port>}, \texttt{<tcp:Interface>} and \texttt{<tcp:Version>}. The \texttt{<tcp:Port>} element is mandatory and should contain an integer corresponding to the TCP port to listen to. The \texttt{<tcp:Interface>} element is optional and is meant to identify the network interface to bind to. It is currently not used. The \texttt{<tcp:Version>} element is used to specify IP version. It is optional and should if present contain the single digit 4 or 6.
}{}

\paragraph{TLS MCC}
The server TLS MCC enables ...

\ifthenelse{\boolean{brieftechdesc}}{
This MCC needs to be configured with a host certificate as well as trusted CA certificates.
}{}

\ifthenelse{\boolean{verbtechdesc}}{
The
}{}
